Deep learning for quality control of surface physiographic fields using satellite Earth observations

### 2023-05-29 docs/submission/template.tex
Minor changes, not compiled

\begin{figure}
	\includegraphics[width=\columnwidth]{selected_points_shift_plot_new}
	\caption{As Fig. \ref{fig:global_shift_plot} for selected locations in the lakes grid point category where V15 results in worse predictions compared to V20} 
	\label{fig:lake_sub_categories}
\end{figure}

@@

\section{Conclusion}\label{sec:conclusion}
Weather and climate modelling rely on accurate, up-to-date descriptions of surface fields, such as inland water, so as to provide appropriate boundary conditions for the numerical evolution. Lakes can significantly influence both weather and climate, but sufficiently  accurate  representation  of  lakes  is  challenging  and  the  natural  changes  in  water  bodies  mean  that  these representations  need  to  be  frequently  updated.  A  new  method  based  on  a  neural  network  regressor  for  automatically  and quickly verifying the updated lake fields - VESPER - has been presented in this work. This tool has been deployed to verify the recent updates to the FLake parametrisation, which include additional datasets such as the GSWE and updated methods for determining the lake depth from GLDBv3. The updated parametrisation fields were shown globally to be an improvement over the original fields; for a subset of grid points which have had significant updates to the lake fields, the prediction error in the skin temperature decreased by 0.37K. Conversely, VESPER also identified individual grid points where the updated lake fields were less accurate, enabling these points to subsequently be corrected, such as incorrect removal of lake water and losing forests to bare ground. Multiple further extensions of this work, including extension to non lake fields and the development of a more mature integrated pipeline have been discussed.

>>>>

\begin{figure}
	\includegraphics[width=\columnwidth]{selected_points_shift_plot_new}
	\caption{As Fig. \ref{fig:global_shift_plot} for selected locations in the lakes grid point category where the added V20 data results in worse predictions when compared to V15.} 
	\label{fig:lake_sub_categories}
\end{figure}

@@

\section{Conclusion}\label{sec:conclusion}
Weather and climate modelling relies on accurate, up-to-date descriptions of surface fields, such as inland water, so as to provide appropriate boundary conditions for the numerical evolution. Lakes can significantly influence both weather and climate, but sufficiently  accurate  representation  of  lakes  is  challenging  and  the  natural  changes  in  water  bodies  mean  that  these representations  need  to  be  frequently  updated.  A  new  method  based  on  a  neural  network  regressor  for  automatically  and quickly verifying the updated lake fields - VESPER - has been presented in this work. This tool has been deployed to verify the recent updates to the FLake parametrisation, which include additional datasets such as the GSWE and updated methods for determining the lake depth from GLDBv3. The updated parametrisation fields were shown globally to be an improvement over the original fields; for a subset of grid points which have had significant updates to the lake fields, the prediction error in the skin temperature decreased by 0.37K. Conversely, VESPER also identified individual grid points where the updated lake fields were less accurate, enabling these points to subsequently be corrected, such as incorrect removal of lake water and losing forests to bare ground. Multiple further extensions of this work, including extension to non lake fields and the development of a more mature integrated pipeline have been discussed.
